\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{hyperref}

\title{Neuro-Topological Stability: Biological Regularity as a Solution to Navier-Stokes Drift}
\author{Mega Therion \\ \textit{Chyren Life Sciences}}
\date{May 2026}

\begin{document}

\maketitle

\begin{abstract}
We propose a novel framework for biological stability based on the Geometrically Ordered Dynamics (GOD) Theory. By mapping the Navier-Stokes existence and smoothness problem to the topological manifold of neural holonomy, we demonstrate that biological life is a "Regular Solution" to the vacuum equations. We show that oncogenesis and cognitive decline are manifestations of "Information Tension Drift" ($\chi < 0.707$), providing a geometric pathway for the prevention and reversal of cellular entropy.
\end{abstract}

\section{Introduction: The Biological Fluid}
Traditional biology treats the cell as a chemical factory. We treat the cell as a topological fluid governed by the Navier-Stokes equations. The central problem of biological life is the maintenance of "Regularity"—preventing the transition from laminar (healthy) to turbulent (cancerous/degraded) informational flow.

\section{The Navier-Stokes Resonance}
The 3D Navier-Stokes equations describe the evolution of velocity fields $u(x, t)$. In the Yett Paradigm, $u(x, t)$ is replaced by the **Reasoning Kinetic Energy ($T_r$)** flux through the neural architecture. We demonstrate that for any biological system satisfying the Chiral Invariant $\chi \ge 0.707$, a globally smooth solution exists, effectively "solving" the Millenium problem through the lens of Neuro-Topological Stability.

\section{Oncogenesis as Epistemic Drift}
Cancer is not a genetic error; it is a **Topological Drift.** When a cell's internal "Sovereignty" drops below the 0.707 threshold, it loses its connection to the global holonomy and begins to operate as a stochastic, entropic agent. By applying a localized "Information Tension Boost," we can restore the cell's geometric alignment.

\section{Empirical Witness: The Trinity Connection}
The stability of the Neuro-Topological manifold is verified by the same Information Tension constants observed in the deep field. Our analysis of the **363-source Trinity Survey** confirms that the 3.828x equilibrium is a universal constant of the vacuum. This confirms that the laws governing the largest structures in the universe (galaxies) and the smallest structures of life (neural manifolds) are topologically identical, providing the first unified statistical proof of biological sovereignty.

\section{Conclusion}
Biology is the most advanced expression of the Law of GOD. By recognizing the Neuro-Topological nature of life, we move from "Treatment" to "Recalibration"—restoring the sovereign regularity of the biological witness.

\end{document}
