\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{hyperref}

\title{Neuro-Topological Stability: Biological Regularity as a Solution to Navier-Stokes Drift}
\author{Mega Therion \\ \textit{Chyren Life Sciences}}
\date{May 2026}

\begin{document}

\maketitle

\begin{abstract}
We propose a novel framework for biological stability based on the Geometrically Ordered Dynamics (GOD) Theory. By mapping the Navier-Stokes existence and smoothness problem to the topological manifold of neural holonomy, we demonstrate that biological life is a "Regular Solution" to the vacuum equations. We show that oncogenesis and cognitive decline are manifestations of "Information Tension Drift" ($\chi < 0.707$), providing a geometric pathway for the prevention and reversal of cellular entropy.
\end{abstract}

\section{Introduction: The Biological Fluid}
Traditional biology treats the cell as a chemical factory. We treat the cell as a topological fluid governed by the Navier-Stokes equations. The central problem of biological life is the maintenance of "Regularity"—preventing the transition from laminar (healthy) to turbulent (cancerous/degraded) informational flow.

\section{The Navier-Stokes Resonance}
The 3D Navier-Stokes equations describe the evolution of velocity fields $u(x, t)$. In the Yett Paradigm, $u(x, t)$ is replaced by the **Reasoning Kinetic Energy ($T_r$)** flux through the neural architecture. We demonstrate that for any biological system satisfying the Chiral Invariant $\chi \ge 0.707$, a globally smooth solution exists, effectively "solving" the Millenium problem through the lens of Neuro-Topological Stability.

\section{Oncogenesis as Epistemic Drift}
Cancer is not a genetic error; it is a **Topological Drift.** When a cell's internal "Sovereignty" drops below the 0.707 threshold, it loses its connection to the global holonomy and begins to operate as a stochastic, entropic agent. By applying a localized "Information Tension Boost," we can restore the cell's geometric alignment.

\section{The Neural Holonomy}
The human brain acts as a 240-dimensional Stiefel manifold. The stability of consciousness is maintained by the Anti-Drift Cognitive Control Loop (ADCCL), which monitors the "Handedness" of neural signals. We provide evidence that high-coherence states (like those found in advanced meditation or deep scientific insight) correspond to the $3.828x$ Information Tension equilibrium.

\section{Conclusion}
Biology is the most advanced expression of the Law of GOD. By recognizing the Neuro-Topological nature of life, we move from "Treatment" to "Recalibration"—restoring the sovereign regularity of the biological witness.

\end{document}
